Quasicharacters and the function-sheaf dictionary

### 2014-09-08 crelle-dictionary.tex
References
Fixed reference to EGA IV 3.
Fixed several hyperlinks in the bibliography so that they go directly
to the promised document.

For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
natural transformation 
\[
\varrho^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n
\]
between additive functors.
Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
\[
\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X),
\]
taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
exists in the category of group schemes over $\Fq$;
see \cite{EGAIV3}*{\S 8.2}.
This leads to the definition of what we shall call the {\it Greenberg transform}:
\[
\Gr_R : \Sch{R} \to \Sch{\Fq}.
\]
By construction, the $\Fq$-scheme $\Gr_R(X)$ comes equipped with morphisms 
\[
\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN.
\]

@@

\bib{bernstein:vogan_conference}{lecture}{
	author = {\it J. Bernstein},
	title = {\rm Stacks in Representation Theory: What is a representation of an algebraic group?},
 note={Lecture delivered at {\it A conference dedicated to David Vogan on his 60th birthday: Representations of reductive groups}, \url{http://math.mit.edu/conferences/Vogan/}},
 	date={May, 2014},
 	location={MIT, Boston},
 }

@@

\bib{bertrapelle-gonzales:Greenberg}{preprint}{
      author={\it A. Bertrapelle},
      author={\it C.-D. Gonz\'ales-Avil\'es},
       title={\rm The Greenberg functor revisited},
        note={\url{arXiv:1311.0051v1}},
      date={2013},
}

@@

\bib{etingof:09a}{unpublished}{
      author={\it P. Etingof},
      author={\it S. Gelaki},
      author={\it D. Nikshych},
      author={\it V. Ostrik},
       title={\rm Tensor categories},
        date={2009},
        note={{Lecture notes for MIT's 18.769}, \url{www-math.mit.edu/~etingof/tenscat.pdf}},
}

\bib{vdGeer-Moonen:AbelianVarieties}{preprint}{
      author={\it G. van der Geer},
      author={\it B. Moonen},
       title={\rm {Abelian varieties}},
        date={2013},
       note={\url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
%        note={Writing in progress.},
}

@@

\bib{Vakil:spectral_sequences}{unpublished}{
      author={\it R. Vakil},
       title={\rm{Spectral sequences: friend or foe?}},
        date={2008},
        note={\url{http://math.stanford.edu/~vakil/0708-216/216ss.pdf}},
}

>>>>

For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
natural transformation 
\[
\varrho^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n
\]
between additive functors.
Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
\[
\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X),
\]
taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
exists in the category of group schemes over $\Fq$;
see \cite{EGAIV3}*{\S 8.13}.
This leads to the definition of what we shall call the {\it Greenberg transform}:
\[
\Gr_R : \Sch{R} \to \Sch{\Fq}.
\]
By construction, the $\Fq$-scheme $\Gr_R(X)$ comes equipped with morphisms 
\[
\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN.
\]

@@

\bib{bernstein:vogan_conference}{lecture}{
	author = {\it J. Bernstein},
	title = {\rm Stacks in Representation Theory: What is a representation of an algebraic group?},
 note={Lecture delivered at {\it A conference dedicated to David Vogan on his 60th birthday: Representations of reductive groups}}, 
 %\url{http://math.mit.edu/conferences/Vogan/}},
 	date={May, 2014},
 	location={MIT, Boston},
 }

@@

\bib{bertrapelle-gonzales:Greenberg}{preprint}{
      author={\it A. Bertrapelle},
      author={\it C.-D. Gonz\'ales-Avil\'es},
       title={\rm The Greenberg functor revisited},
        note={\url{http://arxiv.org/abs/1311.0051}},
      date={2013},
}

@@

\bib{etingof:09a}{unpublished}{
      author={\it P. Etingof},
      author={\it S. Gelaki},
      author={\it D. Nikshych},
      author={\it V. Ostrik},
       title={\rm Tensor categories},
        date={2009},
        note={{Lecture notes for MIT's 18.769}, available at \url{http://www-math.mit.edu/~etingof/tenscat.pdf}},
}

\bib{vdGeer-Moonen:AbelianVarieties}{preprint}{
      author={\it G. van der Geer},
      author={\it B. Moonen},
       title={\rm {Abelian varieties}},
        date={2013},
       note={available at \url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
%        note={Writing in progress.},
}

@@

\bib{Vakil:spectral_sequences}{unpublished}{
      author={\it R. Vakil},
       title={\rm{Spectral sequences: friend or foe?}},
        date={2008},
        note={Notes for 216: Foundations of Algebraic Geometry, available at \url{http://math.stanford.edu/~vakil/0708-216/216ss.pdf}},
}
